---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# guideR

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/larmarange/guideR/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/larmarange/guideR/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/larmarange/guideR/graph/badge.svg)](https://app.codecov.io/gh/larmarange/gguideR)
[![CRAN status](https://www.r-pkg.org/badges/version/guideR)](https://CRAN.R-project.org/package=guideR)
<!-- badges: end -->

`guideR` package is a companion for the manual *guide-R : Guide pour l’analyse de données d’enquêtes avec R* available at <https://larmarange.github.io/guide-R/>.

`guideR` implements miscellaneous functions introduced in *guide-R* to
facilitate statistical analysis.

## Installation & Documentation

To install **stable version**:

```{r eval=FALSE}
install.packages("guideR")
```

Documentation of stable version: <https://larmarange.github.io/guideR/>

To install **development version**:

```{r eval=FALSE}
# install.packages("pak")
pak::pak("larmarange/guideR")
```

Documentation of development version: <https://larmarange.github.io/guideR/dev/>

## Compute proportions 

```{r}
titanic <- Titanic |> dplyr::as_tibble() |> tidyr::uncount(n)

library(guideR)

titanic |> proportion(Class, .conf.int = TRUE)

titanic |> proportion(Survived, .by = Class)
```

